---
output:
  word_document:
    reference_docx: report_template_v1.5.dotx
  pdf_document: default
---

```{r setup, include=FALSE}

# ------------------------------------------------------------------------------
# 20/03/2025 Updated for HAWG 2025 (FB); Rmarkdown. 
# ------------------------------------------------------------------------------
library(knitr)
knitr::opts_chunk$set(comment = NA)

library(icesTAF)

library(FLCore)
library(stockassessment)
library(FLSAM)

library(tidyverse)
library(icesSAG)  # install.packages("icesSAG")
library(pander)

model.path      <- file.path(".",'model')
output.path      <- file.path(".",'output')
report.path      <- file.path(".","report")

# Data settings

# single fleet data
runName <- 'NSAS_HAWG2026'
wg      <- "HAWG2026"

load(file.path(model.path,paste0(runName,'_sf.RData')))
name(NSH) <- runName

# multifleet data
load(file.path(model.path,paste0(runName,'_mf.RData')))
name(NSH3f) <- runName

load('../2026_her.27.3a47d_forecast/data/input_2026_sf.RData')

rpHAWG2026   <- data.frame(refpoint = c("fmsy",'Fsq','Flim','Fpa',"Blim",'Bpa',"msyBtrigger"),
                      value    = c(0.23,NA,0.39,0.23,828874,1049521,1100000),
                      wg       = rep("HAWG2026", 7))

rpIBP2021   <- data.frame(refpoint = c("fmsy",'Fsq','Flim','Fpa',"Blim",'Bpa',"msyBtrigger"),
                      value    = c(0.31,NA,0.4,0.31,874198,956483,1232828),
                      wg       = rep("IBPNSherring2021", 7))

rpWKPELA2018   <- data.frame(refpoint = c("fmsy",'Fsq','Flim','Fpa',"Blim",'Bpa',"msyBtrigger"),
                      value    = c(0.26,NA,0.34,0.30,800000,900000,1400000),
                      wg       = rep("WKPELA2018", 7))

rpAll <- rbind(rpHAWG2026, rpIBP2021,rpWKPELA2018)

rpAll <- rpAll %>% pivot_wider(names_from = refpoint,values_from = value)

panderOptions('keep.line.breaks', TRUE)

```

**Section 2.6.1 Input data**

**Table 2.6.1.2 North Sea herring input data. Maturity at age.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('data/maturity.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.1.3 North Sea herring input data. Natural mortality at age.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('data/natmort.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.1.4 North Sea herring input data. Stock weight at age.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('data/wstock.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.1.5 North Sea herring input data. Catch weight at age.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('data/wcatch.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.1.6 North Sea herring input data. Catch at age.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('data/catage.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.1.7 North Sea herring input data. HERAS survey index at age.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('data/survey_heras.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.1.8 North Sea herring input data. IBTS0 survey index at age.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('data/survey_ibts_0.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.1.9 North Sea herring input data. IBTSQ1 survey index at age. This index is normalized Using the data from DATRAS following the method described in the stock annex**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('data/survey_ibts_q1.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.1.10 North Sea herring input data. IBTSQ3 survey index at age. This index is normalized Using the data from DATRAS following the method described in the stock annex**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('data/survey_ibts_q3.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.1.11 North Sea herring input data. LAI index from the IHLS larvae survey for the Southern North Sea component (Downs). The columns corresponds to survey time windows: 0=16-31Dec, 1=01-15Jan, 2=16-31Jan.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('data/survey_lai_sns.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.1.12 North Sea herring input data. LAI index from the IHLS larvae survey for the Central North Sea component (Banks). The columns corresponds to survey time windows in: 0=01-15Sep, 1=16-30Sep, 2=01-15Oct, 3=16-31Oct.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('data/survey_lai_cns.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.1.13 North Sea herring input data. LAI index from the IHLS larvae survey for the Bunchan component. The columns corresponds to survey time windows in: 0=01-15Sep, 1=16-30Sep.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('data/survey_lai_bun.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.1.14 North Sea herring input data. LAI index from the IHLS larvae survey for the Orkney/Shetland component. The columns corresponds to survey time windows in: 0=01-15Sep, 1=16-30Sep.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('data/survey_lai_orsh.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Section 2.6.2 Single fleet assessment**

**Table 2.6.2.1 North Sea herring single fleet assessment. observation variance per data source and at age.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

df.temp <- as.data.frame(obs.var(NSH.sam))
row.names(df.temp) <- NULL

pander::pandoc.table(df.temp,
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.2.2 North Sea herring single fleet assessment. Catchabilities at age.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

df.temp <- as.data.frame(catchabilities(NSH.sam))
row.names(df.temp) <- NULL

pander::pandoc.table(df.temp,
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.2.3 North Sea herring single fleet assessment. Numbers at age.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('output/natage_sf.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.2.4 North Sea herring single fleet assessment. Harvest at age.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('output/fatage_sf.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.6.2.5 North Sea herring single fleet assessment. Analytical retrospective (Mohn Rho).**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('output/mohn_rho_sf.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

**Table 2.6.2.6 North Sea herring single fleet assessment. Assessment summary.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('output/summary_sf.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

**Table 2.6.2.7 North Sea herring single fleet assessment. SAM model control object.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

print(NSH.ctrl)

```

\newpage

**Section 2.7.1 Short term forecast results**

**Table 2.7.1. North Sea herring. Intermediate year (2025) assumptions for the stock.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

df.temp <- as.data.frame(t(read.csv('../2026_her.27.3a47d_forecast/report/ImY_assumptions.csv',check.names = FALSE)))
colnames(df.temp)   <- 'value'
df.temp <- df.temp[rownames(df.temp) != 'Basis',]
df.temp <- as.data.frame(t(df.temp))
colnames(df.temp) <- c(paste0('F 2-6 (wr) (',ac(range(NSH)['maxyear']+1),')'),
                         paste0('SSB (',range(NSH)['maxyear']+1,')'),
                         paste0('Rage (wr) 0 (',range(NSH)['maxyear']+1,')'),
                         paste0('Rage (wr) 0 (',range(NSH)['maxyear']+2,')'),
                         paste0('Total catch (',range(NSH)['maxyear']+1,')'))
#df.temp$basis       <- c(paste0('Based on estimated catch',range(NSH)['maxyear']+1,')'),
#                         'Calculated based on catch constraint (in tonnes)',
#                         'Estimated by assessment model (in thousands)',
#                         paste0('Weighted mean over ',range(NSH)['maxyear']+1-10,'-',range(NSH)['maxyear']+1,'(in thousands)'),
                         #'Estimated realized catch of autumn spawning herring de- rived from agreed TACs for A-D fleets, the proportion of NSAS herring in the catch (for A, C and D fleets), the transfer of TAC to the North Sea (C fleet) and the uptake of the by- catch quota (for B and D fleets).')

rownames(df.temp) <- NULL

pander::pandoc.table(df.temp,
                     style="simple", split.tables=200, justify="right", missing=".")

```

**Table 2.7.2. North Sea herring. Intermediate year (2026) results.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('../2026_her.27.3a47d_forecast/report/ImY_table.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

**Table 2.7.3. North Sea herring. reference points.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(rpAll,
                     style="simple", split.tables=200, justify="right", missing=".")

```

**Table 2.7.4. North Sea herring. TACs to catches variables.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

catchAreaTab            <- read.taf("../2026_her.27.3a47d_forecast/bootstrap/initial/data/stf_NSAS_catches.csv") # historical C fleet WBSS/NSAS split (Henrik Mosegaard)

TACTab            <- read.taf("../2026_her.27.3a47d_forecast/bootstrap/initial/data/stf_NSAS_TAC.csv")

catchAreaTab$C.tot.DtY <- catchAreaTab$A+catchAreaTab$B+catchAreaTab$C_NSAS+catchAreaTab$C_WBSS+catchAreaTab$D_NSAS+catchAreaTab$D_WBSS+catchAreaTab$IVaE_WBSS
catchAreaTab$C.NSAS.DtY <- catchAreaTab$A+catchAreaTab$B+catchAreaTab$C_NSAS+catchAreaTab$D_NSAS
catchAreaTab$C.WBSS.DtY <- catchAreaTab$C_WBSS+catchAreaTab$D_WBSS+catchAreaTab$IVaE_WBSS

catchAreaTab$NSAS_WBSS_C.split <- catchAreaTab$C.NSAS.DtY/catchAreaTab$C.tot.DtY

df.temp <- as.data.frame(c(TACTab$all[TACTab$year == 2026],560,catchAreaTab$NSAS_WBSS_C.split[catchAreaTab$year == 2025]))
colnames(df.temp)   <- 'value'
df.temp$description <- c('TAC for herring in Areas 4, 7.d, 3.a',
                         'EU fishing opportunities for WBSS in Division 3.a',
                         '2025 proportion of NSAS herring in catches in Areas 4, 7.d, 3.a')
df.temp$basis       <- c('Value from the intermediate year (2026)',
                         'Value from the intermediate year (2026)',
                         'Value from the terminal year (2025)')

rownames(df.temp) <- NULL

pander::pandoc.table(df.temp,
                     style="simple", split.tables=200, justify="right", missing=".")

```

\newpage

**Table 2.7.5. North Sea herring. Final scenario table.**

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

pander::pandoc.table(as.data.frame(read.csv('../2026_her.27.3a47d_forecast/report/forecast_final.csv',check.names = FALSE)),
                     style="simple", split.tables=200, justify="right", missing=".")

```

